\chapter{Abstract}
The EMS-Software should allow a professional event management at all given times. The core premise is to manage users and tickets in combination with events.
Influencers and Promoters, which are mainly People with a big reach on social media, are the newest type of marketing who can promise a quick way to generate attention for events.
This App should create a platform to enable management of these Influencers and Promoters in an easy and comprehensible way, the result of that is a better way to coordinate the marketing of future events.
Additionally, the App simplifies and improves the organizational part of ticket sales. The app differentiates between two Roles, Promoters and Admins.

The Application is segmented into three main pages, where only two are accessible by a promoter.
Each promoter has a profile with their name, a profile picture, and a description.
This profile is customizable by the promoters themselves. The name cannot be changed by a promoter.
The main page contains all current events. All events that are assigned to a promoter to sell tickets are shown here. The Promoter can click on an event and get routed to a detailed page of the chosen event.
Here, the promoter can update his current number of cards sold. For each sold card or package (a collection of cards), the promoter earns goodie-points.
These goodie-points can then be traded for predetermined goodies, for example a freed drink for 10 points, on the event-detail page.

The last page is the admin terminal. As the name implies, this page is only accessible by the admins of EMS. On this site, an admin can create or deactivate a new user or assign a user to an event.
Additionally, events can be created and ticket types, packages and rewards for goodie-points can be defined.

Disclaimer: All provided sources and links have been checked as of 20.4.2021, 16:00 UTC+1 for accuracy and integrity.
They reflect the latest state of knowledge in their respective fields at the given date.
Changes to the sources made after given point of time are not incorporated into the document.
If changes were made, the document is outdated and needs to be udpated.
The provided dates in des sources where created with the help of an own programmed JavaScript.